\section{Ethics Statement}
\label{app:ethics}
\begingroup\sloppy
This research raises several ethical considerations:
\fussy\endgroup

\begin{itemize}
\item \textbf{Cultural Representation and Respect:}
  \begin{itemize}
  \item \begingroup\sloppy\textbf{Cultural Authority:} We acknowledge the ethical complexities of computational systems interpreting culturally significant artifacts, particularly when these systems are developed primarily in Western contexts.\fussy\endgroup
  \item \begingroup\sloppy\textbf{Interpretive Plurality:} We recognize that there is no single "correct" interpretation of cultural symbols, and that diverse perspectives have validity within their cultural contexts.\fussy\endgroup
  \item \begingroup\sloppy\textbf{Persona Construction:} Our persona designs inevitably reflect our own understanding and conceptualization of different expert roles, which may contain unintentional biases or oversimplifications.\fussy\endgroup
  \end{itemize}

\item \textbf{AI Application Considerations:}
  \begin{itemize}
  \item \begingroup\sloppy\textbf{Potential Misuse:} The structured prompting and persona intervention techniques could potentially be misused to generate misleading or biased interpretations if not implemented responsibly.\fussy\endgroup
  \item \begingroup\sloppy\textbf{Algorithmic Bias:} The underlying MLLMs may contain biases that affect their interpretations, particularly across cultural contexts, which our interventions might not fully address.\fussy\endgroup
  \item \begingroup\sloppy\textbf{Transparency:} We emphasize the importance of transparency when deploying AI systems for cultural interpretation, including clear disclosure of the use of persona interventions.\fussy\endgroup
  \item \begingroup\sloppy\textbf{Human Oversight:} While our methods can enhance MLLM capabilities, we advocate for maintaining human expert oversight in sensitive cultural heritage applications.\fussy\endgroup
  \end{itemize}

\item \textbf{Data and Resource Considerations:}
  \begin{itemize}
    \item \begingroup\sloppy\textbf{Data Provenance and Licensing:} The Twelve Months Series paintings were accessed through the National Palace Museum (Taiwan) digital archives under CC BY 4.0 license.\fussy\endgroup
    \item \begingroup\sloppy\textbf{Computational Resources:} Our vector space analysis approach requires significant computational resources, which may limit accessibility for some researchers or institutions.\fussy\endgroup
    \item \begingroup\sloppy\textbf{Expert Knowledge Access:} The development of effective persona cards requires access to specialized knowledge, which may create barriers to implementing similar approaches in other cultural domains.\fussy\endgroup
  \end{itemize}
\end{itemize}

\begingroup\sloppy
We have designed our research to contribute to more culturally sensitive AI applications while acknowledging the limitations of computational approaches to cultural interpretation. Our quantitative framework and structured evaluation methods aim to provide transparent and reproducible results while respecting the complexity and diversity of cultural interpretation.
\fussy\endgroup


